\documentclass[10pt]{developercv} % Default font size, values from 8-12pt are recommended

\begin{document}

\begin{minipage}[t]{0.6\textwidth}
  \vspace{-\baselineskip} % Required for vertically aligning minipages

  {\HUGE\textbf{\MakeUppercase{Eduardo Gomes}}}
  \vspace{5pt}

  {\huge Computer Engineer} % Career or current job title

  \icon{MapMarker}{8}{Belo Horizonte, MG, Brazil}\\

\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
  \vspace{-\baselineskip} % Required for vertically aligning minipages

  \icon{Phone}{8}{+55 31 98269 4939}\\
  \icon{At}{8}{\href{mailto:edu.gmes0@gmail.com}{edu.gmes0@gmail.com}}\\
  \icon{Linkedin}{8}{\href{https://www.linkedin.com/in/eduardog0mes/}{https://www.linkedin.com/in/eduardog0mes/}}\\
\end{minipage}

% \vspace{0.5cm}

\cvsect{Who Am I?}

\begin{minipage}[t]{\textwidth}
  % \vspace{-\baselineskip} % Required for vertically aligning minipages

  I have about 10 yeas of experience in software development. Throughout my career I’ve had the oportunity to work in the development of systems which required programming skills ranging from low- to high-level languages. Not only I could collaborate with key players within my original bachelor’s field, but I could also incorporate valuable professional practices during my exchange time in Germany, and learn interpersonal capacities by venturing in a different area such as the financial market. I’m looking for positions to evolve my career and skills.
\end{minipage}
% \hfill % Whitespace between

\cvsect{Top Technical Skills}

\begin{minipage}[t]{\textwidth}
  % \vspace{-\baselineskip} % Required for vertically aligning minipages

  \begin{skills}
    \skillset{Scripting}{Python, PHP, Java, JavaScript, CSS, C}
    \skillset{Databases}{MySQL, Postgres}
    \skillset{Other}{Git, Python for data science, automation systems, software engineering}
    \skillset{Personal}{Heuristic, didatic experience}
  \end{skills}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
  \entry
  {Jan '17 -- present\\\footnotesize{}\\\footnotesize{}}
  {Entrepreneurship | Trading | Financial Market Analysis Tools}
  {}
  {Software development for the Financial Market, retail trading and e-learning teaching. Key achievements:\\
    \begin{contributionlist}
      \contribution{Own market data analysis tool made with Python consisting of Google Sheets spreadsheet with macros working as a database; offline data processing with Machine Learning and Quantitative Analysis; GUI interface to show market info and real time processed data via RTD/DDE interfaces attached to a market data provider.}
      \contribution{Risk management models to evaluate and track results performance, all concerning trading and market analysis techniques.}
      \contribution{E-learning ecosystem based on wordpress, but extended with PHP/Python to provide a REST interface for private user login area features and  market processed info sharing.}
    \end{contributionlist}\\
    \texttt{Python}\slashsep\texttt{Machine Learning}\slashsep\texttt{Quant. Analysis}\slashsep\texttt{Pandas}\slashsep\texttt{Numpy}}
  \entry
  {Nov '19 -- Aug '20\\\footnotesize{Belo Horizonte, MG, Brazil}}
  {Private Prop. Trading Desk | Futures trader and business partner}
  {}
  {Working with two partners to create a proprietary trading desk. Key achievements:\\
    \begin{contributionlist}
      % \contribution{helped the team to develop and maintain the API and the asynchronous services (messaging platform) of a scalable and high-traffic distributed system.}
      \contribution{Traded futures.}
      \contribution{Developed market analysis tools and models with Python and Google Sheets.}
      \contribution{Initial desk structuring.}
    \end{contributionlist}\\
    \texttt{Python}\slashsep\texttt{Google Sheets}\slashsep\texttt{Macros}\slashsep\texttt{Financial Market}}
  \entry{Jan '18 -- Jan '19\\\footnotesize{Belo Horizonte, MG, Brazil}}
  {System Integrator | Educational Instructor}
  {WM Educacional}
  {
    Started to take up positions for educational trading. Key achievements:\\
    \begin{contributionlist}
      \contribution{Development of result tracking tools via spreadsheets with macros, VBA and Python.}
      \contribution{Trainning programs design for the financial markets and people management (students and instructors).}
    \end{contributionlist}\\
    \texttt{Python}\slashsep\texttt{Spreadsheets}\slashsep\texttt{VBA}}
  \entry{Mar/'16 -- Dec/'17\\\footnotesize{Belo Horizonte, MG, Brazil}\\\footnotesize{Remote}}
  {Trading courses}
  {Scalper Trader | WM Educacional}
  {
    Took courses for retail and educational proprietary desk trading. Key achievements:\\
    \begin{contributionlist}
      \contribution{Learned market and stock exchange fundamentals, including trading psychology and order execution techniques.}
      \contribution{Guest speaker at Scalper Trader annual fair.}
    \end{contributionlist}}\\
  \entry
  {Mar '15 -- Apr '16\\\footnotesize{Manaus, AM, Brazil}}
  {Computer Engineer}
  {IATECAM}
  {
    Embedded systems development using Verilog with Quartus II for Altera FPGAs, C for PIC/PIC32 microcontrollers and Altium software for PCB and schematics.\\
    \texttt{Verilog}\slashsep\texttt{C}\slashsep\texttt{Microcontrollers}}
  \entry{Nov '13 -- Mar '15\\\footnotesize{Manaus, AM, Brazil}}
  {Software Developer}
  {CETELI -- Samsung R\&D Center}
  {
    Development of Android applications using Java and of content management systems using PHP with Yii2 framework, HTML5, CSS3, Javascript and jQuery.\\
    \texttt{Java}\slashsep\texttt{PHP}\slashsep\texttt{JavaScript}\slashsep\texttt{Android}}
  \entry{2009 -- 2010\\\footnotesize{Stuttgart, Germany}}
  {Research Assistant | Studienarbeit}
  {Universität Stuttgart – Institut für Automatisierungs- und Softwaretechnik}
  {
    Key achievements:\\
    \begin{contributionlist}
      \contribution{As research assistant -- Development of an automated scoreboard using C for a dsPIC microcontroller. The system was developed for an automated goalkeeper (GOLIAS).}
      \contribution{With the "Studienarbeit" -- Optimization of a process model of an automated train prototype using RFID. The train control was developed in C and involved speed, light signals, audio and visual signals on a display.}
    \end{contributionlist}\\
    \texttt{Microcontrollers}\slashsep\texttt{Automation Systems}\slashsep\texttt{C}\slashsep\texttt{RFID}}
  \entry{2006 -- 2007\\\footnotesize{Manaus, MG, Brazil}}
  {Software Developer}
  {INdT -- Nokia R\&D Center}
  {Participation in the project "Management of power consumption in open source environments", on which a code analysis tool was implemented using Python to reduce
power consumption of C codes in smartphones.\\
  \texttt{Python}\slashsep\texttt{C}\slashsep\texttt{Open Source}\slashsep\texttt{Power Consumption}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education and Publications}

\begin{entrylist}
  \entry{2001-2013\\\footnotesize{Manaus, \\AM, Brazil}}
  {MSc.\\Electrical Engineering}
  {Federal University of Amazonas}
  {Research area: Ambient Assisted Living}
  \entry{04/2012-02/2013\\\footnotesize{Stuttgart, Germany}}
  {Master Thesis}
  {Institut für Automatisierungs- und Softwaretechnik (IAS)}
  {Research area: Ambient Assisted Living}
  \entry{2005-2010\\\footnotesize{Manaus, AM, Brazil}}
  {Bachelor\\Computer Engineering}
  {Federal University of Amazonas}
  {Research area: Automation Systems}
  \entry{2015\\\footnotesize{Berlin, Germany}}
  {Publication \\"Extending an intelligent medicine cabinet through the use of consumer electronic devices in order to increase the medication adherence"}
  {}
  {IEEE 5th International Conference on Consumer Electronics\\doi: 10.1109/ICCEBerlin.2015.739134}
  \entry{2015\\\footnotesize{Lisbon, Portugal}}
  {Publication \\"An intelligent medicine cabinet proposed to increase medication adherence"}
  {}
  {IEEE 15th International Conference on Healthcare\\doi: 10.1109/HealthCom.2013.6720776}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
  \vspace{-\baselineskip} % Required for vertically aligning minipages

  \cvsect{Languages}

  \begin{skills}
    \skillset{Portuguese}{native}
    \skillset{English}{fluent}
    \skillset{German}{intermediate}
    \skillset{Spanish}{elementary}
  \end{skills}
\end{minipage}

\end{document}
